Community context determines competition vs. facilitation trade-offs in pollination systems

### 2019-07-04 paper/cover-letter.Rnw
Reformat cover letter to fit in two pages
Update Cover Letter for Proceedings B

%-----------------------------------------------------------------------------%
% Letter class
\documentclass[11pt, a4paper]{letter}
\usepackage{hyperref}
\usepackage[backend=bibtex,style=verbose,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{bibliography.bib}
\usepackage{geometry}
\usepackage{setspace}
\geometry{textwidth=31em, textheight=46\baselineskip}
% Name of sender
\name{Fernando Cagua}
% Signature of sender
\signature{Fernando Cagua}
% Address of sender
\address
{
    Fernando Cagua\\
    \href{mailto:efc29@uclive.ac.nz}{efc29@uclive.ac.nz} \\
    +64 20 402 68153 \\
    University of Canterbury, \\
    New Zealand
}
\date{June 14, 2019}
%-----------------------------------------------------------------------------%
\begin{document}
% Name and address of receiver
\begin{letter}
{
    Editorial Office,\\
    Nature Ecology \& Evolution
}
% Opening statement
\opening{Dear Editorial Team,}
% Letter body
\onehalfspacing
<<my-label, eval=TRUE, echo=FALSE>>=
drake::loadd(msc_title)
@

We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{Nature Ecology \& Evolution}.
The main goal of this study is to explore the balance between competition and facilitation in plants belonging to the same community.
The manuscript text is currently organised in the IMRaD structure, but, for future versions, we are more than happy to reformat it and adjust its length to comply with the journal requirements.

@@

This work provides fundamental understanding of plant reproductive biology, while also \emph{calling for a shift in the way we think about pollination in community ecology}, especially from a theoretical perspective.
In contrast to the predominant literature, our study provides compelling evidence that animal-mediated pollination is really a fluid dance between competition and facilitation.
Thus, we believe that this manuscript will be interesting to the broad readership of Nature Ecology \& Evolution.

>>>>

%-----------------------------------------------------------------------------%
% Letter class
\documentclass[11pt, a4paper]{letter}
\usepackage{hyperref}
\usepackage[backend=bibtex,style=verbose,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{bibliography.bib}
\usepackage{geometry}
\usepackage{setspace}
\geometry{textwidth=32em, textheight=47\baselineskip}
% Name of sender
\name{Fernando Cagua}
% Signature of sender
\signature{Fernando Cagua}
% Address of sender
\address
{
    Fernando Cagua\\
    \href{mailto:efc29@uclive.ac.nz}{efc29@uclive.ac.nz} \\
    +64 20 402 68153 \\
    University of Canterbury, \\
    New Zealand
}
\date{July 5, 2019}
%-----------------------------------------------------------------------------%
\begin{document}
% Name and address of receiver
\begin{letter}
{
    Editorial Office,\\
    Proceedings of the Royal Society B
}
% Opening statement
\opening{Dear Editorial Team,}
% Letter body
\onehalfspacing
<<my-label, eval=TRUE, echo=FALSE>>=
drake::loadd(msc_title)
@

We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{Proceedings B}.
The main goal of this study is to explore the balance between competition and facilitation in plants belonging to the same community.

@@

This work provides fundamental understanding of plant reproductive biology, while also \emph{calling for a shift in the way we think about pollination in community ecology}, especially from a theoretical perspective.
In contrast to the predominant literature, our study provides compelling evidence that animal-mediated pollination is really a fluid dance between competition and facilitation.
Some lessons might also be applicable to other biological complex systems where facilitation and competition might be at odds like plant-frugivore and plant-fungus interactions.
Thus, we believe that this manuscript will be interesting to the broad readership of Proceedings B.
